The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-09-24 paper.qmd
got rid of half written sentance (I dont remember what it was supposed to say)
changed weird variance calculation

It would be impossible to display every single uncertainty visualisation in this review, there are far too many so for the sake of clarity, we will focus on the changes made to a single plot, the choropleth map. 
Due to the field's origins and focus in geospatial information visualisation, there have been a large number of suggested variations on the choropleth map that allow authors to include uncertainty. 
While the theoretical approach we outline is useful to all uncertainty visualisations, regardless of their application, we feel that focusing on a single example will help isolate the ideas we are trying to convey. 
We will use these maps to show the effects we are talking about, and highlight the costs and benefits of each approach. 
These examples will need XXX incomplete sentence!! XXX

@@

my_map_data <- my_map_data |>
  dplyr::mutate(temp = 29 - 3*abs(scale(cent_lat) - sin(2*(scale(cent_long)))[,1]), # trend
         notrend = rnorm(n), # no trend
         highvar = runif(n, min=1, max=2), # high variance
         lowvar = runif(n, min=0, max=1), # low variance
         ) |>
  mutate(highvar = highvar^2,
         lowvar = lowvar^2,
         count_id = row_number()) |>
  pivot_longer(cols=highvar:lowvar, names_to = "variance_class", values_to = "variance") |>
  # add bivariate classes to data
  mutate(bitemp = cut(temp, breaks=breaks, labels=seq(8)),
         bivar = cut(variance, breaks=0:4, labels=seq(4)),
         biclass = paste(bitemp, bivar, sep="-"))

>>>>

It would be impossible to display every single uncertainty visualisation in this review, there are far too many so for the sake of clarity, we will focus on the changes made to a single plot, the choropleth map. 
Due to the field's origins and focus in geospatial information visualisation, there have been a large number of suggested variations on the choropleth map that allow authors to include uncertainty. 
While the theoretical approach we outline is useful to all uncertainty visualisations, regardless of their application, we feel that focusing on a single example will help isolate the ideas we are trying to convey. 
We will use these maps to show the effects we are talking about, and highlight the costs and benefits of each approach.

@@

my_map_data <- my_map_data |>
  dplyr::mutate(temp = 29 - 3*abs(scale(cent_lat) - sin(2*(scale(cent_long)))[,1]), # trend
         highvar = runif(n, min=2, max=4), # high variance
         lowvar = runif(n, min=0, max=2), # low variance
         count_id = row_number()) |>
  pivot_longer(cols=highvar:lowvar, names_to = "variance_class", values_to = "variance") |>
  # add bivariate classes to data
  mutate(bitemp = cut(temp, breaks=breaks, labels=seq(8)),
         bivar = cut(variance, breaks=0:4, labels=seq(4)),
         biclass = paste(bitemp, bivar, sep="-"))
